\begin{thebibliography}{100}

\bibitem{xrayTools} U. Eglė, “Diagnostic X-ray hardware,” 2011, (In lithuanian).

\bibitem{bioInspired} M. Woźniak and D. Połap, “Bio-inspired methods modeled for respiratory disease detection from medical images,” Swarm Evol. Comput., vol. 41, pp. 69–96, Aug. 2018.

\bibitem{lungNodules} M. Woźniak, D. Połap, G. Capizzi, G. Lo Sciuto, L. Kośmider, and K. Frankiewicz, “Small lung nodules detection based on local variance analysis and probabilistic neural network,” Comput. Methods Programs Biomed., vol. 161, pp. 173–180, Jul. 2018.

\bibitem{radiodiagnosis} B. V. Daga, V. R. Shah, and S. V. Daga, Radiodiagnosis, nuclear medicine, radiotherapy and radiation oncology. Jaypee Brothers Medical Publishers, 2013.

\bibitem{cancer} A. Berrington de González et al., “Projected Cancer Risks From Computed Tomographic Scans Performed in the United States in 2007,” Arch. Intern. Med., vol. 169, no. 22, p. 2071, Dec. 2009.

\bibitem{comparison} Y. Y. Kim, H. J. Shin, M. J. Kim, and M.-J. Lee, “Comparison of effective radiation doses from X-ray, CT, and PET/CT in pediatric patients with neuroblastoma using a dose monitoring program.,” Diagn. Interv. Radiol., vol. 22, no. 4, pp. 390–4, 2016.

\bibitem{oecd2018} European Commission and OECD, Health at a Glance: Europe 2018 STATE OF HEALTH IN THE EU CYCLE. 2018.

\bibitem{yeonCT} Y. Y. Kim, H. J. Shin, M. J. Kim, and M.-J. Lee, “Comparison of effective radiation doses from X-ray, CT, and PET/CT in pediatric patients with neuroblastoma using a dose monitoring program.,” Diagn. Interv. Radiol., vol. 22, no. 4, pp. 390–4, 2016.

\bibitem{dataRsna} “RSNA Bone Age data set from Kaggle.” [Online]. Available: https://www.kaggle.com/kmader/rsna-bone-age. [Accessed: 01-Mar-2019].

\bibitem{dataNih} “NIH Chest X-rays data set from Kaggle.” [Online]. Available: https://www.kaggle.com/nih-chest-xrays/data. [Accessed: 01-Mar-2019].

\bibitem{dataMura} “Stanford University MURA Dataset: Towards Radiologist-Level Abnormality Detection in Musculoskeletal Radiographs.” [Online]. Available: https://stanfordmlgroup.github.io/competitions/mura/. [Accessed: 01-Mar-2019].

\bibitem{poisson} S. Lee, M. S. Lee, and M. G. Kang, “Poisson–Gaussian Noise Analysis and Estimation for Low-Dose X-ray Images in the NSCT Domain,” Sensors, vol. 18, no. 4, p. 1019, Mar. 2018.

\bibitem{simulNoise} Hanying Li, T. Toth, S. McOlash, Jiang Hsieh, and N. Bromberg, “Simulating low dose CT scans by noise addition,” in 2002 IEEE Nuclear Science Symposium Conference Record, 2002, vol. 3, pp. 1832–1834.

\bibitem{ssim} Z. Wang, A. C. Bovik, H. R. Sheikh, S. Member, E. P. Simoncelli, and S. Member, “Image Quality Assessment: From Error Visibility to Structural Similarity,” vol. 13, no. 4, pp. 1–14, 2004.

\bibitem{a1} N. Johnston et al., “Improved Lossy Image Compression with Priming and Spatially Adaptive Bit Rates for Recurrent Networks,” Mar. 2017.



\end{thebibliography}

%%%%% CLEAR DOUBLE PAGE!
% \newpage{\pagestyle{empty}\cleardoublepage}